\section{Supermanifolds and Graded Manifolds}
\label{sec:supermanifolds}

Similarly to the linear case, we want to generalize the concepts of superspace and graded vector space to the case of manifolds.
For this we start by the definition of supermanifolds.

\begin{definition}
\label{def:supermanifold}
    A \emph{supermanifold} $\mathcal{M}$ is a locally ringed space $(M, \mathcal{O}_M)$, which is locally isomorphic to
    \begin{equation*}
        \Big(\mathcal{U}, C^\infty(\mathcal{U}) \otimes \bigwedge V^*\Big),
    \end{equation*}
    where $\mathcal{U}$ is an open subset of $\mathbb{R}^d$ and $V$ some finite-dimensional real vector space.
\end{definition}

We call the manifold $M$ in the previous definition the \emph{body} and $\mathcal{O}_M$ the $\emph{structure sheaf}$ of $M$.
Notice that a supermanifold has locally the same structure as the algebra we described in \Cref{ex:comm_anticomm}.

Notice also that the isomorphism present in \Cref{def:supermanifold} is a $\mathbb{Z}_2$-graded algebra, which is defined by the parity operator:
\begin{align*}
    |\quad | : 
    \bigoplus_{k \geq 0} C^\infty(\mathcal{U}) \otimes \bigwedge^k V^* 
    &\rightarrow \mathbb{Z}_2 \\
    f \otimes \theta &
    \mapsto |f \otimes \theta| = |\theta| = k \! \! \mod{2}.
\end{align*}

\begin{example}
    The supermanifold having $\mathbb{R}^q$ as body ($q$ even coordinates) and structure sheaf given by
    \begin{equation*}
         C^\infty(\mathbb{R}^q) \otimes \bigwedge \mathbb{R}^p
    \end{equation*}
    ($p$ odd coordinates) is called the \emph{standard supermanifold} and denoted by $\mathbb{R}^{q|p}$.
\end{example}

We now introduce another important structure, that can be combined with the one of supermanifolds.

\begin{definition}
    \label{def:graded_manifold}
    A \emph{graded manifold} is a locally ringed space $\mathcal{M} = (M, \mathcal{O}_M)$, which is locally isomorphic to
    \begin{equation*}
        \Big(\mathcal{U}, C^\infty(\mathcal{U}) \otimes \text{Sym}(V^*) \Big),
    \end{equation*}
    where $\mathcal{U}$ is an open subset of $\mathbb{R}^d$ and $V$ some finite-dimensional real vector space.
\end{definition}
 In \Cref{def:graded_manifold}, by $\text{Sym}(V^*)$ we denote the set of symmetric powers of $V^*$, i.e. $\text{Sym}(V^*) \coloneqq \left( \text{Sym}^n(V^*) \right)_{n \in \mathbb{N}}$. The $n$-th symmetric power of a vector space $V$ is given by
 \begin{equation*}
     \text{Sym}^n V =
     V^{\otimes n} /
     \left( x_1 \otimes \ldots \otimes x_n - \sigma (x_1 \otimes \ldots \otimes x_n,
     \sigma \in \mathfrak{S}_n \right),
 \end{equation*}
 where $\mathfrak{S}_n$ denotes the $n$-th symmetric group.

The $\mathbb{Z}$-grading of a graded manifold is denoted by gh and named \emph{ghost number}.
In particular, for some function $f$ on a graded manfiold $\mathcal{M}$, we denote by $\text{gh}(f)$ its degree with respect to the $\mathbb{Z}$-grading.
In particular, physical fields have ghost number zero.
This is useful since in field theory, the space of fields can be describes with the structure of a graded manifold.

Instead, the $\mathbb{Z}_2$-grading of a supermanifold corresponds to the commuting and anticommuting coordinates.
In physics language, the property of commuting even coordinates corresponds to bosonic particles, while the anticommuting property of the odd coordinates is specific for fermionic particles.